<<<<<<< HEAD
---
title: "Untitled"
author: "Christian Sirait"
date: "2022-12-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dslabs)
library(janitor)
library(stringr)
library(leaflet)
library(htmlwidgets)
library(tidyverse)
library(dplyr)
library(here)
library(vroom)
library(tidyverse)
library(hablar)
library(dbscan)
library(factoextra)
library(cluster)
library(leaflet)
library(ggthemes)
library(fishualize)
library(fpc)
library(tidyr)
```

```{r}
getwd()
murder <- vroom(here("Crime_Data_from_2020_to_Present.csv"))
murder
```

```{r}
murder <-clean_names(murder)
colnames(murder)
murder <- subset(murder, !is.na(murder$weapon_desc))
murder <- subset(murder, !is.na(murder$crm_cd_2))
murder
```

```{r}
murder
```

```{r}
murder<- murder %>% mutate_if(is.character, ~replace_na(.,"DATA NOT REPORTED"))%>% mutate_if(is.double, ~replace_na(.,0)) 
murder <- murder %>% select (-crm_cd_3,-crm_cd_4,-area)
murder
```

```{r}
lln = min(murder$lon)
uln = max(murder$lon)
llat = min(murder$lat)
ulat = max(murder$lat)

centlon = (lln+uln)/2
centlat = (llat+ulat)/2

leaflet(data = murder) %>% 
  addTiles() %>% 
  setView(lng = -118.243683,lat = 34.052235,zoom =  10) %>% 
  addCircleMarkers(lng = ~murder$lon, 
                   lat = ~murder$lat, 
                   radius =1)
```

```{r}
locs=select(murder,lat,lon)
locs.scaled = scale(locs,center = T,scale = T)

head(locs.scaled)
```
```{r}
kNNdistplot(murder[,24:25], k = 8)
abline(h= 0.007, col = "red", lty = 3)
```

```{r}
mur <- dbscan(murder[,24:25], eps = 0.007, MinPts = 8)
mur
```

```{r}
murder <- murder %>% 
  mutate(clust = mur$cluster)

# membuat pallet color untuk setiap cluster
pallet <- fishualize::fish(n = length(unique(murder$clust)), option = "Bryaninops_natans")
pal <- colorFactor(pallet, domain = unique(murder$clust))

# visualisasi cluser tanpa data noise
leaflet(data = murder[murder$clust !=0,]) %>% 
  addTiles() %>% 
  setView(lng = -118.243683,lat = 34.052235,zoom =  10) %>% 
  addCircleMarkers(lng = ~murder$lon, 
                   lat = ~murder$lat, 
                   radius =1,
                   color = ~pal(murder$clust))

```



```{r}
set.seed(2)
trainIndex = sample(nrow(locs.scaled),size = round(0.8*nrow(locs)))
X_train = locs.scaled[trainIndex,]
y_train = locs.scaled[-trainIndex,]

#model application
dbsc = dbscan(X_train,eps = 0.15,MinPts  = 12)

# Cluster prediction

preds = predict.dbscan(object = dbsc,
               data = X_train,newdata = y_train,
                )
```

```{r}
table(preds)
=======
---
title: "Untitled"
author: "Christian Sirait"
date: "2022-12-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dslabs)
library(janitor)
library(stringr)
library(leaflet)
library(htmlwidgets)
library(tidyverse)
library(dplyr)
library(here)
library(vroom)
library(tidyverse)
library(hablar)
library(dbscan)
library(factoextra)
library(cluster)
library(leaflet)
library(ggthemes)
library(fishualize)
library(tidyr)
```

```{r}
getwd()
murder <- vroom(here("Crime_Data_from_2020_to_Present.csv"))
murder
```

```{r}
murder <-clean_names(murder)
colnames(murder)
murder <- subset(murder, !is.na(murder$cross_street))
murder
```

```{r}
murder
```

```{r}
murder<- murder %>% mutate_if(is.character, ~replace_na(.,"DATA NOT REPORTED"))%>% mutate_if(is.double, ~replace_na(.,0)) 
murder <- murder %>% select (-crm_cd_3,-crm_cd_4,-area)
murder
```

```{r}
lln = min(murder$lon)
uln = max(murder$lon)
llat = min(murder$lat)
ulat = max(murder$lat)

centlat = (llat+ulat)/2
centlon = (lln+uln)/2
sbt = murder
mp = leaflet(sbt) %>%
  setView(centlon,centlat,zoom = 4) %>%
  addProviderTiles("OpenStreetMap") %>%
  addCircleMarkers(lng = sbt$lon,
                   lat = sbt$lat,
                   popup = sbt$area_name,
                   fillColor = "Black",
                   fillOpacity = 1,
                   radius = 4,
                   stroke = F)
mp
```